Ensembler: Enabling high-throughput molecular simulations at the superfamily scale

### 2015-06-22 manuscript/ms.tex
Minor updates to ms

% TODO expand to all human protein kinases?

@@

% TODO? The API is highly flexible, allowing control over many important parameters. Appropriate choices have been set as default values.

% TODO? other tools for analyzing project etc.

@@

The resultant models are available as part of a supplementary dataset which can be accessed \emph{via} the digital object identifier (DOI) \href{https://dx.doi.org/10.5061/dryad.7fg32}{10.5061/dryad.7fg32}.

@@

% TODO what's on the Ensembler 2 roadmap?

>>>>

@@

@@

The resultant models are available as part of a supplementary dataset which can be downloaded from the Dryad Digital Repository (DOI: \href{https://dx.doi.org/10.5061/dryad.7fg32}{10.5061/dryad.7fg32}).

@@
